Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks.

### 2020-06-09 main.Rmd
Added classification results on EffectorP data

@@

@@

\beginsupplement
```{r, bacefftable, echo=FALSE, message = FALSE}

apa_table(
  readr::read_tsv("tables/bacterial_effector_count.tab"),
  digits = 0,
  align = 'c',
  caption = 'Bacterial species contributing to the bacterial effector sequence set retrieved from PHI-Base'
)
```

@@

```{r, hyperparam}
 readr::read_tsv("tables/hyperparamscan_info.tab") %>%
  knitr::kable( "latex", longtable = T, booktabs = T,
           digits = 0,
  align = 'c',
  caption = 'Hyperparameters used in automatic scanning of hyperparameter space and best performing parameters values for each model'
         ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header"), font_size = 7)

>>>>

We are also interested in evaluating positive datasets from other tools on our model and compare the results when the datasets evaluated on their own tool. Table \@ref(tab:accf1scoreeffectorpdata) shows the of accuracy and F1 score values of classification results of three different positive datasets from EffectorP 1.0 and 2.0.

```{r accf1scoreeffectorpdata}
apa_table(
  readr::read_csv("data/processed/acc_f1score_result_effectorp_data_prediction.csv"),
  digits = 4,
  align = 'c',
  caption = 'Accuracy and F1-Score from prediction results of EffectorP data evaluated on Deepredeff and both EffectorP 1.0 and EffectorP 2.0',
  placement = "h"
)
```

@@

```{r effectorpdatacfmat, fig.width=6, fig.height=6, fig.cap="Confusion matrices of classifications made by our fungi model compared with EffectorP 1.0 and EffectorP 2.0 evaluated on both training and validation EffectorP data.", message = FALSE, echo=FALSE}
readr::read_csv("data/processed/conf_mat_effectorp_data_prediction.csv") %>% 
  ggplot2::ggplot() +
  ggplot2::aes(x = Truth, y = Prediction) +
  ggplot2::geom_tile(ggplot2::aes(fill = Freq), colour = "white") +
  ggplot2::geom_text(ggplot2::aes(label = Freq), vjust = 0.5) +
  ggplot2::facet_grid(data ~ tool) +
  ggplot2::scale_fill_viridis_c(begin = 0.2, end = 1) +
  ggplot2::labs(x = "True value", y = "Prediction") +
  ggplot2::coord_fixed()
```

@@

\beginsupplement

```{r, bacefftable, echo=FALSE, message = FALSE}
apa_table(
  readr::read_tsv("tables/bacterial_effector_count.tab"),
  digits = 0,
  align = 'c',
  caption = 'Bacterial species contributing to the bacterial effector sequence set retrieved from PHI-Base',
  placement = "h"
)
```

@@

```{r, hyperparam}
readr::read_tsv("tables/hyperparamscan_info.tab") %>%
  knitr::kable(
    "latex", 
    longtable = T, 
    booktabs = T,
    digits = 0,
    align = 'c',
    caption = 'Hyperparameters used in automatic scanning of hyperparameter space and best performing parameters values for each model'
  ) %>%
  kableExtra::kable_styling(latex_options = c("repeat_header"), font_size = 7)
```
